---
title: "Overview of bigram semantic distance computations"
author: "Celia Litovsky, Ann Marie Finley, Bonnie Zuckerman, & Jamie Reilly"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of bigram semantic distance computations}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#devtools::install_github("Reilly-ConceptsCognitionLab/semdistflow") # install package if haven't already
library(semdistflow)
library(tidytext)
library(tidyverse)
library(knitr)
library(kableExtra)
library(stringr)
library(zoo)
library(stringi)
library(printr)
```


# Preparing Your Texts

Each text you wish to process should be saved as a .txt file. Your texts should be stored in one folder. The file names in a given folder should be unique. 

# Loading your texts
```{r}
mytexts <- readtxt(here("mytexts")) # input path name to .txt files, read in files
```

The resulting data.frame should have two columns "doc_id" and "doc_text". 
```{r}
print(mytexts)
```

If you wish to use this package but want to read in your data another way, you must ensure that you have the columns names "doc_id" and "doc_text". The "doc_id" column but be unique for each text. You may include other columns if you wish. 

# "Cleaning" your data 
```{r clean,}
mytexts.clean <- cleanme(mytexts, replace_pronoun = TRUE) # performs all cleaning functions on the texts in mytexts. replace_pronoun = TRUE changes pronouns to simple antecedent (e.g., he -> person). replace_pronoun = FALSE keeps pronouns as-is
```

Notice new column "doc_clean" has been added with the cleaned text

```{r, clean table print, echo=FALSE}
head(mytexts.clean)
```

# Computing cosine distances
```{r clean,}
mytexts.dist <- distme(mytexts.clean)
```

# Plot bigram cosine distance values over each text
GloWCA (GloVe) plotting
```{r}
mytexts.dist <- mytexts.dist %>% 
  mutate(text_name = sub('.*\\/', '', doc_id))

mytexts.dist<- mytexts.dist %>%
  group_by(doc_id) %>% 
  mutate(id = row_number())

glove_plot <- ggplot(mytexts.dist, aes(x = id, y=Glowca_CosRev0Score)) +  geom_line(color="#02401BD9") + facet_grid(~text_name, scales="free")

glove_plot
```

SemDist15 plotting
```{r}
mytexts.dist <- mytexts.dist %>% 
  mutate(text_name = sub('.*\\/', '', doc_id))

mytexts.dist<- mytexts.dist %>%
  group_by(doc_id) %>% 
  mutate(id = row_number())

semdist15_plot <- ggplot(mytexts.dist, aes(x = id, y=Sd15_CosRev0Score)) +
  geom_line(color="#EBCC2AA3") + facet_grid(~text_name, scales="free")

semdist15_plot
```
